Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-05-04 paper.tex

Some treaty verification scenarios require estimating historical fissile
material production based on records of facility operation and material
transfer.  If the measurements of facility operation and material transfer are
subject to uncertainty, the total production quantities will then also be
uncertain, creating an opportunity for undetected diversion.  This study seeks
to understand which measures of facility operation have the most impact on the
uncertainty of fissile material production across a complete fuel cycle.  A
``Total Monte Carlo'' approach will be applied to the Cyclus fuel cycle simulator
\cite{cyclus} to estimate output metrics uncertainty caused by individual
facility uncertainties.

@@

To estimate the uncertainty on fuel cycle output metrics, a ``Total Monte
Carlo'' approach has been applied. In the following, output metric uncertainty
corresponds to the Standard Deviation of the output metrics over about 200
different simulations. For each deployed facilities, the uncertainty associated
parameters have been a normally distributed with an artificially large standard
deviation of $10\%$.

To pursuit this work, both the Cycamore\cite{cycamore} package and the
CyCLASS\cite{cyclass} have been updated to deal with uncertainty in different
operational parameters of their different facility.  Table
\ref{tab:package_uncertainty} summarize all the modification implemented in the
different facilities present in Cycamore and CyCLASS.

@@

Note: the fuel enrichment is determined by a fuel fabrication model\cite{leniau} which
express a fissile fraction required in the fuel to reach a target
burnup at the end of irradiation. In this study, the uncertainty on the fuel
enrichment is not applied directly on the effective enrichment but on the target
parameter (the burnup), which leads to to a fuel enrichment uncertainty close to
$10\%$.

>>>>

Some treaty verification scenarios require estimating historical fissile
material production based on records of facility operation and material
transfer.  If the measurements of facility operation and material transfer are
subject to uncertainty, the total production quantities will then also be
uncertain, creating an opportunity for undetected diversion.  This study seeks
to understand which measures of facility operation have the most impact on the
uncertainty of fissile material production across a complete fuel cycle.  An
approaching using Total Monte Carlo methodology will be applied to the Cyclus
fuel cycle simulator
\cite{cyclus} to estimate output metrics uncertainty caused by individual
facility uncertainties.

% I don't think Total Monte Carlo should be in quotes

@@

To estimate the uncertainty on fuel cycle output metrics, a Total Monte
Carlo approach has been applied. In the following, output metric uncertainty
corresponds to the Standard Deviation of the output metrics over about 200
different simulations. For each deployed facilities, the uncertainty associated
parameters have been a normally distributed with an artificially large standard
deviation of $10\%$.

To pursuit this work, both the Cycamore\cite{cycamore} package and the
CyCLASS\cite{cyclass} have been updated to deal with uncertainty in several
operational parameters of their associated facilities.  Table
\ref{tab:package_uncertainty} summarizes all modificatiosn implemented in the
range of facilities present in Cycamore and CyCLASS.

@@

It must be noted that for this work, the fuel enrichment was determined by a
fuel fabrication model\cite{leniau} which
calculates the fissile fraction required in the fuel to reach a target
burnup at the end of irradiation. In this study, the uncertainty on the fuel
enrichment is not applied directly on the effective enrichment but on the target
parameter (the burnup), which leads to to a fuel enrichment uncertainty close to
$10\%$.
